Based on polling as of 27 October 2024, Harris expects to win on xxx%, leads Trump by xx% in 2024 US election

### 2024-10-30 paper/paper.qmd
update data cleaning part

---
title: "Based on polling as of 27 October 2024, Harris expects to win on xxx%, leads Trump by xx% in 2024 US election"
subtitle: "Weighted Linear Regression Analysis of Aggregated Poll Data: Utilizing National Polls indicator, Recency of Polls, Sample Size, Pollster Quality Rate, and Poll Frequency as Predictors."
author: 
  - Diana Shen
  - Jinyan Wei
  - Jerry Yu
thanks: "Code and data are available at: [https://github.com/DianaShen1224/Forecast-2024-US-election](https://github.com/DianaShen1224/Forecast-2024-US-election)."
date: today
date-format: long
abstract: "This paper predicts the outcome of the 2024 U.S. presidential election using a statistical model based on aggregated polling data for Kamala Harris and Donald Trump. We employ multi-level regression with post-stratification (MRP) using demographic predictors to estimate voter support. The analysis addresses polling biases and proposes an idealized survey methodology with a $100,000 budget. Our results offer insights into voter behavior and suggest improvements for future election forecasting models."
format: pdf
number-sections: true
bibliography: references.bib
editor: 
  markdown: 
    wrap: 72
---

@@

In this data-cleaning process, we focus on refining raw polling data to
enhance its quality and relevance for subsequent analysis. The dataset
is first loaded and cleaned using the janitor package to standardize
column names, ensuring consistency. We then filter the data to include
only relevant columns and remove any rows with missing values in
critical fields such as numeric_grade, pct, sample_size, and end_date.
Specifically, we isolate the polling data for Kamala Harris and Donald
Trump, applying a condition to keep only high-quality polls with a
numeric grade of 2 or higher since we find out that the mean of the
numeric grade is 2.175 while the median is 1.9.

For state-level polls, we address any placeholder states marked as "--"
by converting them to NA. A national poll indicator is created,
assigning a value of 1 for national polls and 0 for state-specific ones.
Dates are converted to a standard format using the lubridate package to
ensure correct handling in analyses. We calculate recency weights based
on how many days have passed since the poll ended, applying an
exponential decay to give more weight to recent polls. A sample size
weight is also implemented, capping the weights at a maximum of 2,300
responses to reflect the reliability of larger sample
sizes[@nyt_polling_averages]. Finally, the cleaned datasets for both
candidates are saved in CSV format for further modeling and analysis.
This systematic approach ensures that the data is accurate, complete,
and ready for insightful analysis.

>>>>

---
title: "Based on polling as of 27 October 2024, Harris expects to win on xxx%, leads Trump by xx% in 2024 US election"
subtitle: "Weighted Linear Regression Analysis of Aggregated Poll Data: Utilizing National Polls indicator, Population, and Pollster as Predictors."
author: 
  - Diana Shen
  - Jinyan Wei
  - Jerry Yu
thanks: "Code and data are available at: [https://github.com/DianaShen1224/Forecast-2024-US-election](https://github.com/DianaShen1224/Forecast-2024-US-election)."
date: today
date-format: long
abstract: "This paper predicts the outcome of the 2024 U.S. presidential election using a statistical model based on aggregated polling data for Kamala Harris and Donald Trump. We employ multi-level regression with post-stratification (MRP) using demographic predictors to estimate voter support. The analysis addresses polling biases and proposes an idealized survey methodology with a $100,000 budget. Our results offer insights into voter behavior and suggest improvements for future election forecasting models."
format: pdf
number-sections: true
bibliography: references.bib
editor: 
  markdown: 
    wrap: 72
---

@@

In this data-cleaning process, we focus on refining raw polling data to enhance its quality and relevance for subsequent analysis. The dataset is initially loaded and cleaned using the janitor package to standardize column names, ensuring consistency throughout. We then filter the data to retain only relevant columns and eliminate any rows with missing values in critical fields, including numeric_grade, pct, sample_size, and end_date.

Specifically, we isolate the polling data for Kamala Harris and Donald Trump, applying a condition to include only high-quality polls with a numeric grade of 2 or higher, given that the mean of the numeric grade is 2.175 and the median is 1.9.

For state-level polls, we handle any placeholder states marked as "--" by converting them to NA. A national poll indicator is generated, assigning a value of 1 for national polls and 0 for state-specific ones. Dates are standardized using the lubridate package to ensure accurate handling in subsequent analyses.

Recency weights are calculated based on the number of days elapsed since the poll ended, utilizing an exponential decay function to give greater weight to more recent polls. Additionally, a sample size weight is implemented, capping the weights at a maximum of 2,300 responses to reflect the reliability of larger sample sizes.

Finally, the cleaned datasets for both candidates are saved in CSV format for further modeling and analysis. This systematic approach guarantees that the data is accurate, complete, and ready for insightful analysis.
